Bayesian statistics and swine flu

### 2009-09-24 docs/pandemic/bayesPandemic.rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@409 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{frame}
\frametitle{Prior graphs}
<<priorGraph, fig=false,results=tex>>=
priors= readPrior("bayesPandemicPriors.txt")
plotPrior(priors$InfOns, file="InfOns", tex=TRUE)
#$
@
\vspace*{-0.8cm}
Density and hazard curves are shown for combinations of the 2.5\% and 97.5\% quantiles of each parameter's prior distribution.
\end{frame}

>>>>

\begin{frame}[fragile]
\frametitle{Infection type priors}

\begin{verbatim}
PS Priors
transition	distribution	taub1	taub2	priorMean	upper95
probs	fatality	psPrior	   2	   0.05	  0.01	   0.02
probs	hosp    	psPrior	   2	   0.05	  0.01	   0.02
\end{verbatim}

\begin{frame}
\frametitle{Prior graphs}
<<priorGraph, fig=false,results=tex>>=
priors = readPrior("bayesPandemicPriors.txt")
plotPrior(priors$InfOns, file="InfOns", tex=TRUE)
#$
@
\vspace*{-0.8cm}
Density and hazard curves are shown for combinations of the 2.5\% and 97.5\% quantiles of each parameter's prior distribution.
\end{frame}
